Single cell resolution landscape of equine peripheral blood mononuclear cells reveals diverse cell types including T-bet+ B cells.

### 2020-12-14 analysis/paper/paper.Rmd
update readme formatting #2

# Set up R environment
```{r echo = FALSE, message=FALSE}
### Load packages necessary for script
library(renv)
library(Matrix)
library(AnnotationDbi)
library(tibble)
library(gtools)
library(cowplot)
library(gdata)
library(clustree)
library(future)
library(rrtools)
library(rlang)
library(uwot)
library(Seurat)
library(sctransform)
library(ggnetwork)
library(RColorBrewer)
library(ggrepel)
library(readxl)
library(ggpubr)
library(lemon)
library(scales)
library(edgeR)
library(dplyr)
library(patchwork)
library(ape)
library(mgsub)
library(jntools)
library(BiocManager)
library(viridis)
library(ggtree)
library(ggforce)
library(legocolors)
library(openxlsx)
library(cluster)
library(factoextra)
library(GEOquery)
library(ComplexHeatmap)
library(circlize)
library(here)
library(reshape2)
library(tidyr)
library(modelr)

>>>>

# Set up R environment
```{r echo = FALSE, message=FALSE}
### Load packages necessary for script
library(renv)
library(details)
library(Matrix)
library(AnnotationDbi)
library(tibble)
library(gtools)
library(cowplot)
library(gdata)
library(clustree)
library(future)
library(rrtools)
library(rlang)
library(uwot)
library(Seurat)
library(sctransform)
library(ggnetwork)
library(RColorBrewer)
library(ggrepel)
library(readxl)
library(ggpubr)
library(lemon)
library(scales)
library(edgeR)
library(dplyr)
library(patchwork)
library(ape)
library(mgsub)
library(jntools)
library(BiocManager)
library(viridis)
library(ggtree)
library(ggforce)
library(legocolors)
library(openxlsx)
library(cluster)
library(factoextra)
library(GEOquery)
library(ComplexHeatmap)
library(circlize)
library(here)
library(reshape2)
library(tidyr)
library(modelr)
